### 2023-09-05 sections/3-datasets.tex
fixed unfortunate typos

\section{Datasets And Benchmarking}
\label{sec:datasets-and-distance-functions}

@@

We compared against FAISS 1.7.4~\cite{johnson2019billion} (IVF and HNSW) and a BLAS-accelerated implementation of na\"ive search as reported in~\cite{johnson2019billion}.

@@

% \begin{itemize} 
%     \item DEEP1B (Cosine): $\sim$1 billion 96-dimensional deep descriptors to 
%     \item Fashion-MNIST (Euclidean): 60,000 784-dimensional vector representations of images of clothing items
%     \item GIST (Euclidean): 1 million 960-dimensional image descriptors 
%     \item GloVe (Cosine): $\sim$1.2 million 25-dimensional vector representations of words
%     \item Kosarak (Jaccard): $\sim$75 thousand ~28 thousand-dimensional binary vectors representing user clickstreams
%     \item MNIST (Euclidean): 60,000 784-dimensional vector representations of images of handwritten digits
%     \item NYTimes (Cosine): 290,000 256-dimensional vector representations of words
%     \item SIFT (Euclidean): 1 million 128-dimensional image descriptors
%     \item Last.fm (Cosine): $\sim$292, 000 65-dimensional vector representations of songs
% \end{itemize}

\begin{table}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Datasets used in benchmarks.}
    \label{table:datasets:summary}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|l|l|l|}
    \hline
    \textbf{Dataset} & \textbf{Distance}  &\textbf{Cardinality}  & \textbf{Dim.}  \\
    &                &                  &                         \\
    \hline
    nytimes          & cosine              & 290,000            & 256       \\
    \hline
    fashion-mnist    & euclidean              & 60,000             & 784       \\
    \hline 
    gist             & euclidean              & 1,000,000          & 960       \\
    \hline
    glove-25         & cosine              & 1,183,514          & 25        \\
    \hline
    glove-100        & cosine              & 1,183,514          & 100       \\
    \hline
    sift             & euclidean              & 1,000,000          & 128       \\
    \hline
    deep-image       & cosine              & 9,990,000          & 96        \\
    \hline
    mnist            & euclidean              & 60,000             & 784       \\
    \hline
    glove-50         & cosine              & 1,183,514          & 50        \\
    \hline
    lastfm           & cosine              & 292,385            & 65        \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table}

>>>>

\section{Datasets And Benchmarking}
\label{sec:datasets-and-benchmarks}

@@

We compared against FAISS~\cite{johnson2019billion} (IVF and HNSW) and a BLAS-accelerated implementation of na\"ive search as reported in~\cite{johnson2019billion}.

@@

\begin{table}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Datasets used in benchmarks.}
    \label{table:datasets:summary}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|l|l|l|}
                    \hline
                    \textbf{Dataset} & \textbf{Distance}  &\textbf{Cardinality}  & \textbf{Dim.}  \\
                    \hline
                    fashion-mnist    & euclidean              & 60,000             & 784       \\
                    \hline 
                    gist             & euclidean              & 1,000,000          & 960       \\
                    \hline
                    glove-25         & cosine              & 1,183,514          & 25        \\
                    \hline
                    glove-50         & cosine              & 1,183,514          & 50        \\
                    \hline
                    glove-100        & cosine              & 1,183,514          & 100       \\
                    \hline
                    sift             & euclidean              & 1,000,000          & 128       \\
                    \hline
                    deep-image       & cosine              & 9,990,000          & 96        \\
                    \hline
                    mnist            & euclidean              & 60,000             & 784       \\
                    \hline
                    lastfm           & cosine              & 292,385            & 65        \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table}

### 2023-09-05 sections/4-results.tex
fixed unfortunate typos

We did not run any of the competitor’s algorithms. We lifted the reported numbers from the ann-benhmarks site and their interactive plots. We made sure to use the same aws instance as they did so its a fair comparison

Tables \ref{table:results:ann-10} and \ref{table:results:ann-100} show the results of our benchmarking against FAISS, bruteforce-blas, and HNSW. Our throughput values for these algorithms comes from the ANN benchmarks website's interactive plots, from which we can assess the throughput of each algorithm at a given recall value. We

We report the highest throughput value for each algorithm at a recall value of 1.0. We report the recall value for each algorithm at the highest throughput value. We report the mean and median speedup factor of CAKES over each algorithm.
For $k= 10$, we report a mean $7654\times$ (median $1200\times$) speedup over faiss-ivf, a mean $11325\times$ (median $2821\times$) speedup over bruteforce-blas, 
and a mean $485\times$ (median $417\times$) speedup over HNSW. 
For $k=100$, we report a mean $4479\times$ (median $3456\times$) speedup over faiss-ivf, a mean $16010\times$ (median $13548\times$) speedup over bruteforce-blas, and a mean $403\times$ (median $372\times$) speedup over HNSW.

@@

We notice that the mean and median speedup factors differ significantly for all methods, which suggests that the speedup factor is heavily dataset-dependent on the dataset; in particular, across all algorithms, and both values of $k$, CAKES exhibits particularly high speedup factors with SIFT and GIST, under Euclidean distance. As GIST was designed to be a difficult dataset for classifiers~\cite{Lee2019PracticalLP} , CAKES's strong performance with this dataset is particularly encouraging. Further investigation of CAKES's performance on other challenging or adversarial datasets is warranted.

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=10$}
    \label{table:results:ann-10}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
    \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
    \cline{2-9}
    &               Recall & QPS      & Recall & QPS    & Recall & QPS    & Recall & QPS \\
    \hline
    fashion-mnist & 1.000  & 188.03    & 1.000 & 52.91  & 1.000* & 339.74 & 1.000 & 141,800 \\
    \hline
    gist          & 1.000 & 3.55  & 1.000 & 2.63        & 0.953 & 149.58  & 1.000 & 76,420 \\
    \hline
    glove-25      & 1.000 & 78.78  & 1.000 & 33.52      & 1.000 & 552.67  & 0.798 & 94,580 \\
    \hline
    glove-100     & 1.000 & 21.16  & 1.000 & 16.52      & 0.998 & 155.90  & 0.904 & 4,566 \\
    \hline
    sift          & 1.000 &  24.52 & 1.000 & 16.40      & 1.000 & 275.07  & 1.000 & 357,400 \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=100$. Other methods did not report results for glove-25. Asterisk on recall value indicates that the algorithm had imperfect recall greater than or equal to 0.9995}
    \label{table:results:ann-100}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
    \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
    &                    Recall & QPS  & Recall & QPS     & Recall & QPS      & Recall & QPS \\
    \hline
    fashion-mnist  & 1.000 & 111.47    & 1.000* & 16.02   & 1.000* & 277.80   & 1.000 & 71,370 \\ 
    \hline
    gist           & 1.000 & 2.70      & 1.000* & 0.80    & 0.995 & 59.71     & 1.000 & 29,090 \\
    \hline
    glove-25       & -- & --           & --     & --      & -- & --           & 0.851 & 49,350 \\
    \hline
    glove-100      & 1.000* &  19.04   & 1.000* & 7.52    & 0.987 & 92.58     & 0.905 & 4,384 \\
    \hline
    sift           & 1.000 &  23.50    & 1.000  & 6.51    & 1.000* & 179.14   & 1.000 & 147,400 \\                                                 
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES and Speedup Factor over Naive Linear Search, $k=10$}
    \label{table:results:ann-alt-10}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|l|l|l|l|}
    \textbf{Dataset} & \textbf{CAKES Throughput} & \textbf{Speedup Factor over Linear} \\
    \hline
    deep-image       & 232.1                     & 37.2      \\
    \hline
    mnist            & 129,300                   & 101.9      \\
    \hline
    glove-50         & 10,950                    & 12.28      \\
    \hline 
    glove-200        & 2,290                     & 8.55     \\
    \hline
    lastfm           & 13,950                    & 4.55           \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES and Speedup Factor over Naive Linear Search, $k=100$}
    \label{table:results:ann-alt-100}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|l|l|l|l|l|}
    \textbf{Dataset} & \textbf{CAKES Throughput} & \textbf{Speedup Factor over Linear} \\
    \hline
    deep-image             &157.3 &25.74             \\
    \hline
    mnist                 &71,090 &56.63      \\
    \hline
    glove-50               & 8,867 & 9.84      \\
    \hline 
    glove-200              & 2,264 & 8.49    \\
    \hline
    lastfm                 & 13,950     &4.55                               \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

>>>>

We did not run any of the competitor's algorithms.
We lifted the reported numbers from the ann-benchmarks site and their interactive plots.
We made sure to use the same aws instance as they did so its a fair comparison.

Tables \ref{table:results:ann-10} and \ref{table:results:ann-100} show the results of our benchmarks against FAISS, bruteforce-blas, and HNSW.
The throughput values for these algorithms comes from the ANN benchmarks website's interactive plots, from which we can assess the throughput of each algorithm at a given recall value.

We report the highest throughput value for each algorithm at a recall value of 1.0.
We report the mean and median speedup factor of CAKES over each algorithm.
For $k= 10$, we report a mean $7,654 \times$ (median $1,200 \times$) speedup over faiss-ivf, a mean $11,325 \times$ (median $2,821 \times$) speedup over bruteforce-blas, and a mean $485 \times$ (median $417 \times$) speedup over HNSW. 
For $k=100$, we report a mean $4,479 \times$ (median $3,456 \times$) speedup over faiss-ivf, a mean $16,010 \times$ (median $13,548 \times$) speedup over bruteforce-blas, and a mean $403 \times$ (median $372 \times$) speedup over HNSW.

@@

We note that the mean and median speedup factors differ significantly for all methods, which suggests that the speedup factor is heavily dataset-dependent;
in particular, across all algorithms, and both values of $k$, CAKES exhibits particularly high speedup factors with SIFT and GIST, under Euclidean distance.
As GIST was designed to be a difficult dataset for classifiers~\cite{Lee2019PracticalLP}, CAKES's strong performance with this dataset is particularly encouraging.
Further investigation of CAKES's performance on other challenging or adversarial datasets is warranted.

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=10$}
    \label{table:results:ann-10}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \cline{2-9}
                    &               Recall & QPS      & Recall & QPS    & Recall & QPS    & Recall & QPS \\
                    \hline
                    fashion-mnist & 1.000  & 188.03    & 1.000 & 52.91  & 1.000* & 339.74 & 1.000 & 141,800 \\
                    \hline
                    gist          & 1.000 & 3.55  & 1.000 & 2.63        & 0.953 & 149.58  & 1.000 & 76,420 \\
                    \hline
                    glove-25      & 1.000 & 78.78  & 1.000 & 33.52      & 1.000 & 552.67  & 0.798 & 94,580 \\
                    \hline
                    glove-100     & 1.000 & 21.16  & 1.000 & 16.52      & 0.998 & 155.90  & 0.904 & 4,566 \\
                    \hline
                    sift          & 1.000 &  24.52 & 1.000 & 16.40      & 1.000 & 275.07  & 1.000 & 357,400 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=100$. Other methods did not report results for glove-25. Asterisk on recall value indicates that the algorithm had imperfect recall greater than or equal to 0.9995.}
    \label{table:results:ann-100}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    &                    Recall & QPS  & Recall & QPS     & Recall & QPS      & Recall & QPS \\
                    \hline
                    fashion-mnist  & 1.000 & 111.47    & 1.000* & 16.02   & 1.000* & 277.80   & 1.000 & 71,370 \\ 
                    \hline
                    gist           & 1.000 & 2.70      & 1.000* & 0.80    & 0.995 & 59.71     & 1.000 & 29,090 \\
                    \hline
                    glove-25       & -- & --           & --     & --      & -- & --           & 0.851 & 49,350 \\
                    \hline
                    glove-100      & 1.000* &  19.04   & 1.000* & 7.52    & 0.987 & 92.58     & 0.905 & 4,384 \\
                    \hline
                    sift           & 1.000 &  23.50    & 1.000  & 6.51    & 1.000* & 179.14   & 1.000 & 147,400 \\                                                 
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES and Speedup Factor over Naive Linear Search, $k=10$}
    \label{table:results:ann-alt-10}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|l|l|l|l|}
                    \hline
                    \textbf{Dataset} & \textbf{CAKES Throughput} & \textbf{Speedup Factor over Linear} \\
                    \hline
                    deep-image       & 232.1                     & 37.2      \\
                    \hline
                    mnist            & 129,300                   & 101.9      \\
                    \hline
                    glove-50         & 10,950                    & 12.28      \\
                    \hline 
                    glove-200        & 2,290                     & 8.55     \\
                    \hline
                    lastfm           & 13,950                    & 4.55           \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES and Speedup Factor over Naive Linear Search, $k=100$}
    \label{table:results:ann-alt-100}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|l|l|l|l|l|}
                    \hline
                    \textbf{Dataset} & \textbf{CAKES Throughput} & \textbf{Speedup Factor over Linear} \\
                    \hline
                    deep-image        & 157.3                    & 25.74                               \\                            
                    \hline
                    mnist             & 71,090                   & 56.63                               \\
                    \hline
                    glove-50          & 8,867                    & 9.84                                \\
                    \hline 
                    glove-200         & 2,264                    & 8.49                                \\
                    \hline
                    lastfm            & 13,950                   & 4.55                                \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

### 2023-09-05 sections/5-discussion.tex
fixed unfortunate typos

We have presented CAKES, a method for fast $k$-nearest-neighbors search that can adapt to a variety of distance functions.
CAKES provides exact $k$-NN when the distance function in use is a metric (particularly, when it obeys the triangle inequality).
CAKES is most effective when datasets are not uniform and do not obey a ``simple'' distribution such as Gaussian, but rather adhere to ``interesting'' low-dimensional manifolds even when embedded in a high-dimensional space; thus, CAKES is best when the manifold hypothesis is upheld.

Unlike locality-sensitive hashing (LSH) approaches, which require a novel hashing function for each distance metric in use, CAKES is extensible to any user-provided distance function.
Also unlike LSH approaches, CAKES guarantees perfect precision and recall as long as the distance function in use is a \emph{metric}; that is, it obeys the properties of identity, symmetry, and the triangle inequality.
As mentioned in Section~\ref{sec:introduction}, this should not be conflated with having $k$-NN itself provide perfect \emph{inference} accuracy.

In comparison to other methods, While CAKES has perfect recall for distance metrics, it exhibits worse recall under non-metrics (specifically, cosine distance). This bears further investigation, but likely stems from how heavily the $k$-NN and clustering algorithms depend on the triangle inequality.
Preliminary results suggest that when FAISS and HNSW are tuned for lower recall, they are still slower than CAKES in all cases.

Some of the questions raised by this study suggest that future work is justified; a comparison across more datasets and larger datasets is clearly in order, as is further analysis with distance functions that existing methods such as FAISS do not support, such as Wasserstein distance~\cite{vallender1974calculation} (particularly for arbitrary dimensionality), as Tanimoto distance~\cite{bajusz2015tanimoto}, which is particularly applicable to computing distances based on maximal common subgraphs of molecular structures.
Incorporating these or other distance functions in CAKES only requires providing a Rust implementation of the distance function.
For all datasets benchmarked, the auto-tuning method selected repeated $\rho$-nearest neighbor (Section~\ref{subsubsec:methods:knn-search:repeated-rnn}).
However, in limited testing on synthetic datasets obeying simple distributions, this was not always the case.
We seek to evaluate these approaches on many more datasets and distance metrics; it could be that repeated $\rho$-NN is always best (and thus the autotuning is unnecessary), but such a determination is premature.

In future work, we plan to investigate compression by representing differences at each level of the
binary tree, particularly for string or genomic data, where all differences are discrete.
When we descend a level in the cluster tree, it takes fewer bits to encode each point in terms of the center. 
However, each descent of a level in the cluster tree increases the bit-cost of specifying a particular cluster. 
This presents the following tradeoff: \emph{How do we algorithmically determine the depth to which we should cluster a dataset to achieve optimal compression?} 
In our future work, we will explore which properties of the dataset and of clusters can inform this optimal depth.
Along with compression, we would like to add the ability to perform ``online'' updates as new points are added to a dataset.

We also plan to use CAKES with anomaly detection. Our anomaly detection tool, CHAODA~\cite{ishaq2021clustered}, uses 
a variety of methods in an ensemble to determine an anomaly score for a point. We would like to explore the effectiveness of using
distance to the $k$-th nearest neighbor as an additional method in our ensemble.

The source code for CAKES is available under an MIT
license at https://github.com/URI-ABD/clam.

>>>>

We have presented CAKES, a method for fast $k$-nearest-neighbors search that can adapt to a variety of distance functions.
CAKES provides exact recall with $k$-NN when the distance function in use is a metric (particularly, when it obeys the triangle inequality).
CAKES is most effective when datasets are not uniform and do not obey a ``simple'' distribution such as Gaussian, but rather adhere to ``interesting'' low-dimensional manifolds even when embedded in a high-dimensional space;
thus, CAKES works best when the manifold hypothesis is upheld.

In comparison to other methods, while CAKES has perfect recall for distance metrics, it exhibits worse recall under non-metrics (specifically, cosine distance). This bears further investigation, but likely stems from how heavily the $k$-NN and clustering algorithms depend on the triangle inequality when discarding clusters from consideration.
However, the ann-benchmarks results show that even when FAISS and HNSW are tuned for lower recall, they are still slower than CAKES in all cases.

The questions raised by this study suggest several avenues for future work.
A comparison across more datasets and larger datasets is clearly in order, as is further analysis with distance functions that existing methods such as FAISS do not support, such as Wasserstein distance~\cite{vallender1974calculation} (particularly for arbitrary dimensionality), and Tanimoto distance~\cite{bajusz2015tanimoto}, which is particularly applicable to computing distances based on maximal common subgraphs of molecular structures.  % TODO: Add Lev, NW, SW
Incorporating these or other distance functions in CAKES only requires a Rust implementation of the distance function.

For all datasets benchmarked, the auto-tuning method selected repeated $\rho$-nearest neighbor (Section~\ref{subsubsec:methods:knn-search:repeated-rnn}).
However, during limited testing on synthetic datasets obeying simple distributions, this was not always the case.
We seek to evaluate these approaches on many more datasets and distance metrics;
it could be that repeated $\rho$-NN is always best (and thus the auto-tuning is unnecessary), but such a determination would be premature.

In future work, we plan to investigate compression by representing differences at each level of the binary tree, particularly for string or genomic data, where all differences are discrete.
When we descend some levels in the cluster tree, it takes fewer bits to encode each point in terms of the center because the radii decrease.
However, each descent of a level in the cluster tree increases the bit-cost of specifying a particular cluster. 
This presents the following tradeoff:
\emph{How do we algorithmically determine the depth to which we should cluster a dataset to achieve optimal compression?} 
In our future work, we will explore which properties of the dataset and of clusters can inform this optimal depth.

We would like to add the ability to perform ``online'' updates to the tree as points are added to or deleted from a dataset.
This would enable CAKES to be used in a streaming environment.

We also plan to use CAKES with anomaly detection.
Our anomaly detection tool, CHAODA~\cite{ishaq2021clustered}, uses a variety of methods in an ensemble to determine an anomaly score for a point.
We would like to explore the effectiveness of using the distribution of distances among the $k$-th nearest neighbors as an additional method in our ensemble.

CLAM and CAKES are implemented in Rust and their source code is available under an MIT license at https://github.com/URI-ABD/clam.
